---
output: 
  html_document:
    includes:
      in_header: iframe_resizer.html
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
library(gradethis)
knitr::opts_chunk$set(echo = FALSE)
```

Store the sample space of a 8-sided die into `dice_8`. Then, run a simulation where you throw two 8-sided dice over 6 trials. Store the simulation results into `simul_two_dice8_6trials`. 

```{r simul-ex, exercise=TRUE}
dice_8 <-

simul_two_dice8_6trials
```

<div id="simul-ex-hint">
Did you create a sample space for `dice_8`?

Have you used the `replicate()` and `sample()` function inside? 

Did you remember to specify `replace= FALSE` inside `sample()`?
</div>

```{r simul-ex-solution}
dice_8 <- c(1:8)

simul_two_dice8_6trials<- replicate(6, sample(dice_8, 2, replace=TRUE))

```

```{r simul-ex-code-check}
grade_code()
```
Now, store the sample space for a coin flip. Define 1= Heads and 0= Tails. Flip 5 coins for 20 trials, and store the result in `simul_5coin_20trial`.

Finally, we want to know how many of the 5 coins were `heads`. Since `1` represents `heads`, we can use `colSums()` in order to add up the total number of heads in each column. Store that result as number_heads_20_trials. 

What was the average number of heads that you flipped, out of 20 trials? 

``` {r simul-ex-2, exercise=TRUE}
coin
  
simul_5coin_20trial
  
number_heads_20_trials 

# Find the mean number of heads here:  

```

<div id="simul-ex-2-hint">
coin <- c(...)
  
simul_5coin_20trial <- replicate(... , sample(... , ... , replace=TRUE))

number_heads_20_trials <- colSums(...)

**Find the mean number of heads here:  **

mean(...)
</div>


```{r simul-ex-2-solution}
coin<- c(0:1)

simul_5coin_20trial <- replicate(20, sample(coin, 5, replace=TRUE))

number_heads_20_trials <- colSums(simul_5coin_20trial)  

number_heads_20_trials <-  
# Find the mean number of heads here:   
mean(number_heads_20_trials)
```


```{r simul-ex-2-code-check}
grade_code()

```