---
output: 
  html_document:
    includes:
      in_header: iframe_resizer.html
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
library(readr)
library(kableExtra)
library(gradethis)
knitr::opts_chunk$set(echo = FALSE)
gradethis::gradethis_setup()
```

## Warm Up

Generate the following vectors and store them by their given names:

1. one_to_ten: 1, 2, 3, 4, 5, 6, 7, 8, 9, 10

2. evens_to_20: 0  2  4  6  8 10 12 14 16 18 20

3. IBET: "Integrated", "Biology", "English", "Technology"

4. twice_one_to_ten: a vector from #1 that multiplies every element by 2.


```{r warm-up, exercise=TRUE, exercise.cap="Warm Up"}
#1

#2

#3

#4

```

```{r warm-up-hint}
#1
one_to_ten<- "Use the : Operator"
#2
evens_to_20<- "Use seq()"
#3
IBET <- "Use c()"
#4
twice_one_to_ten<- "Use vector operations"
```

```{r warm-up-solution}
#1
one_to_ten<- 1:10
#2
evens_to_20<- seq(from=0, to=20, by=2)
#3
IBET<- c("Integrated", "Biology", "English", "Technology")
#4
twice_one_to_ten<- one_to_ten*2
```

```{r warm-up-code-check}
grade_code()
```

## Exercise 1

Recreate the following dataframe, and store it under the name `tiktokers`.

```{r tiktokers kable, echo=FALSE, fig.cap="Table for Chapter 4 Exercise"}
urlfile<- 'https://github.com/kaisamng/RGuides_learnr/blob/main/Chapters_2_to_4_Exercises/ch2_4_data.RData?raw=true'
load(url(urlfile))
knitr::kable(tiktokers, caption="Table for Chapter 4 Exercise", booktabs=FALSE) %>%
  kable_styling(position= "center")
```

```{r exercise-1, exercise=TRUE, exercise.cap="Exercise 1"}
# Recreate the following Dataframe here:




```

```{r exercise-1-hint}
best_cats <- data.frame(
  variable_1= c(),
  variable_2= c(),
  variable_3= c()
)
```

```{r exercise-1-solution}
tiktokers<- data.frame(
  user= c("khaby.lame", "charlidamelio", "bellapoarch", "addisonre", "willsmith", "zachking", "kimberly.loaiza", "tiktok", "cznburak", "dixiedamelio"),
  rank= c(1:10),
  brand= c(rep(FALSE, 7), TRUE, rep(FALSE, 2)),
  followers_mill= c(142.9, 142.3, 90.1, 87.9, 72, 68.7, 63.6, 62.9, 59, 57.4),
  likes_mill= c(2286.9, 10960.3, 2096.8, 5682.3, 437.3, 866.9, 3723.9, 268.8, 1057.7, 3202.8)
)

```

```{r exercise-1-code-check}
grade_code()
```


## Exercise 2

1. Write code that selects every other tiktoker (1st, 3rd, 5th...)

2. Write code that selects only the tiktoker that is a brand account.

3. Write code that selects any tiktoker that is *not* a brand, and only their `likes_mill` and `followers_mill` column.

4. Write code that selects all tiktokers that have more than 1 billion likes. (In this case, since the `likes` column is in terms of millions, you want to select all tiktokers that are greater than 1000.)

```{r exercise-2, exercise=TRUE, exercise.cap="Exercise 2"}
#This prints out the number of likes that each tiktoker has, in millions.
tiktokers$likes_mill

#Write the solution for #1 here.


#Write the solution for #2 here.


#Write the solution for #3 here.


#Write the solution for #4 here.



```



```{r exercise-2-hint}
#This prints out the number of likes that each tiktoker has, in millions.
tiktokers$likes_mill

#Write the solution for #1 here.
seq(from=1, to=20, by=3)

#Write the solution for #2 here.


#Write the solution for #3 here.


#Write the solution for #4 here.



```

```{r exercise-2-solution}
#This prints out the number of likes that each tiktoker has, in millions.
tiktokers$likes_mill

#Write the solution for #1 here.
tiktokers[seq(from=1, to=10, by=2), ]

#Write the solution for #2 here.
tiktokers[tiktokers$brand %in% TRUE,]

#Write the solution for #3 here.
tiktokers[tiktokers$brand %in% FALSE, c("likes_mill", "followers_mill")]

#Write the solution for #4 here.
tiktokers[tiktokers$likes_mill> 1000, ]

```

```{r exercise-2-code-check}
grade_code()
```

``` {r exercise-2-setup}
urlfile<- 'https://github.com/kaisamng/RGuides_learnr/blob/main/Chapters_2_to_4_Exercises/ch2_4_data.RData?raw=true'
load(url(urlfile))
```

## Exercise 3

Now, you will use the periodic_table data. It has already been loaded for you.

```{r}
head(periodic_table)
```

1. Select the row whose element `name` is "Beryllium." 

2. Select all rows whose element has a `group` of `1`, and whose `state_at_stp` is `Solid`. Use the `%in%` and `&` operator.

3. Select all rows whose element has a `description` of `Halogen`, or whose `group` is greater than `17`. Return only the `atomic_number`, `symbol`, `name`, and `state_at_stp` columns.  Given that this single call will return some `NA`s, insert your entire command into the `na.omit()` function. 

```{r exercise-3, exercise=TRUE, exercise.cap="Exercise 3", exercise.diagnostics=FALSE}
#1

#2

#3

```

```{r exercise-3-hint}
#1
periodic_table[... %in% "Beryllium", ]
#2
periodic_table[... & ... , ]
#3
na.omit(periodic_table[... | ...], c(...))
```


```{r exercise-3-solution}
#1
periodic_table[periodic_table$name %in% "Beryllium", ]
#2
periodic_table[periodic_table$group %in% 1 & periodic_table$state_at_stp %in% "Solid", ]
#3
na.omit(periodic_table[periodic_table$description %in% "Halogen" | periodic_table$group > 17, c("atomic_number", "symbol", "name", "state_at_stp")])
```

```{r exercise-3-code-check}
grade_code()
```

```{r exercise-3-setup, include=FALSE, message=FALSE, warning=FALSE}
urlfile<- 'https://github.com/kaisamng/RGuides/blob/main/resources/data/periodic-table-data.csv?raw=true'
periodic_table <- read_csv(url(urlfile))
```

<div data-iframe-height></div>