---
output: 
  html_document:
    includes:
      in_header: iframe_resizer.html
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
library(gradethis)
library(BSDA)
knitr::opts_chunk$set(echo = FALSE)
```

The following exercises will use the `Tv` dataset from the `BSDA` library. [Check out the documentation here.](https://www.rdocumentation.org/packages/BSDA/versions/1.2.1/topics/Tv)

Here are the three variables (column names) in the `Tv` dataset.
```{r colnames}
colnames(Tv)

```

### Exercise 1

```{r exp, echo=FALSE}
question("What is the explanatory variable?",
         answer("state"),
         answer("percent", correct=TRUE),
         answer("test"))
```

```{r response, echo=FALSE}
question("What is the response variable?",
         answer("state"),
         answer("percent"),
         answer("test", correct=TRUE))

```


### Exercise 2

Create a scatter plot of `Tv` to investigate the relationship between the explanatory variable and response variable. For your title and axes labels, use the description of each variable from the data set (from `?Tv`) (so if you were using `percent`, it would be "percent of students who watch more than six hours of TV a day".)

```{r plot, exercise=TRUE, exercise.lines=5}


```


<div id="plot-hint">
Use `plot()`. Remember to specify your `xlab`, `ylab`, and `main`.
</div>

```{r plot-solution, echo=F}
plot(test~percent, data=Tv,
     main="Percent of students that watch more than 6 hours of TV per day versus national math test scores",
     xlab="Percent of students who watch more than six hours of TV a day",
     ylab="State average on National Math Test")

```

```{r plot-code-check, echo=F}
grade_code()
```


### Exercise 3

Create a linear regression model, store it as `reg_model`, and then print it out.

```{r linreg, exercise=TRUE}


```

<div id="linreg-hint">
You probably already used `linreg()`, but you also need to use `summary()`.

Remember that `linreg()` requires you include your formula and data parameters.

</div>

```{r linreg-solution, echo=F}
reg_model <- lm(test~percent, data=Tv)

summary(reg_model)

```

```{r linreg-code-check, echo=F}
grade_code()
```

```{r slope, echo=FALSE}
question("What is the slope of this linear regression line?",
         answer("287.0679"),
         answer("2.6881"),
         answer("106.79"),
         answer("-1.8531", correct=T),
         answer("0.1768"),
         answer("-10.48"))
```


```{r int, echo=FALSE}
question("What is the y-intercept of this linear regression line?",
         answer("287.0679", correct=T),
         answer("2.6881"),
         answer("106.79"),
         answer("-1.8531"),
         answer("0.1768"),
         answer("-10.48"))
```


```{r eq, echo=FALSE}
question("What is the equation of this linear regression line?",
         answer("$\\hat{y}=-1.8531 + 287.0679x$"),
         answer("$\\hat{y}=1.8531x + 287.0679$"),
         answer("$y=-1.8531\\hat{x} + 287.0679$"),
         answer("$\\hat{y}=-1.8531x + 287.0679$", correct=T),
         answer("$\\hat{y}=-1.8531 + 287.0679\\hat{x}$"))
```



### Exercise 4

Using your code from Exercise 2, plot the scatterplot again, and then graph your linear regression from exercise 3 on top. **You will need to copy your code from Exercise 2** into the box below.

Make sure your line is **red**.

```{r lm, exercise=TRUE, exercise.setup="linreg-solution", exercise.lines=6}





```



<div id="lm-hint">
Run the scatter plot command first. Then, run `abline()` separately using the linear model variable you got from exercise 3. 
</div>

```{r lm-solution}
plot(test~percent, data=Tv,
     main="Percent of students that watch more than 6 hours of TV per day versus national math test scores",
     xlab="Percent of students who watch more than six hours of TV a day",
     ylab="State average on National Math Test")
abline(reg_model, col="red")
```


```{r lm-code-check, echo=F}
grade_code()
```


























































































