---
output: 
  html_document:
    includes:
      in_header: iframe_resizer.html
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
library(gradethis)
knitr::opts_chunk$set(echo = FALSE)
```

All questions refer to the Standard Normal Distribution, unless mentioned otherwise.

1. Find the probability of $z < -1.43$.

```{r pnorm-1, exercise=TRUE}


```

<div id="pnorm-1-hint">
Should you be using `pnorm()` or `qnorm()`?

Should the probability be greater than 0.5, or less than 0.5?
</div>


```{r pnorm-1-check}
grade_result(
  pass_if(~identical(.result, pnorm(-1.43)))
)
```



2. Calculate $z> -1.7$


```{r pnorm-2, exercise=TRUE}


```

<div id="pnorm-2-hint">
What percentage represents the entire area under the curve?

If `pnorm` gives you the area starting from the left, how do you find the area starting from the right?

</div>


```{r pnorm-2-check}
grade_result(
  pass_if(~identical(.result, 1-pnorm(-1.7)))
)
```

3. Find the missing number in $P(z<\text{_____})= 0.2$ that would make this equation true.

```{r qnorm-1, exercise=TRUE}


```

<div id="qnorm-1-hint">
Are you given a z-score, or are you given a probability/area?

Are you solving for a right-bound area, or a left-bound area?

Should the z-score be negative, or positive?

</div>


```{r qnorm-1-check}
grade_result(
  pass_if(~identical(.result, qnorm(0.2)))
)
```





4. Find the missing number in $P(z>\text{_____})= 0.7$ that would make this equation true.

```{r qnorm-2, exercise=TRUE}


```

<div id="qnorm-2-hint">
The probability here is greater than 50%. Does that mean $z$ should be left of center, or right of center?

Should the z-score be negative, or positive?

</div>

```{r qnorm-2-check}
grade_result(
  pass_if(~identical(.result, qnorm(0.7)))
)
```



5. Find the value of $z$ such that the positive and negative values of $z$ capture the middle 98% of the data.

```{r qnorm-3, exercise=TRUE}


```


<div id="qnorm-3-hint">
If 98% of the data is in the middle, what percentage is outside the tail?

Are you focused on the area of one tail, or the area of two tails?

</div>


```{r qnorm-3-solution}
# negative ----
qnorm(0.01)

# positive ----
qnorm(0.99)
```


```{r qnorm-3-check}
grade_this({
  pass_if_equal(
    .solution_all[["negative"]],
    "That's right! This is the negative z-value for the LEFT side."
  )
  pass_if_equal(
    .solution_all[["positive"]],
    "That's right! This is the positive z-value for the RIGHT side."    
  )
  fail(hint=FALSE)
})
```















