---
output: learnr::tutorial
  # html_document:
  #   includes:
  #     in_header: iframe_resizer.html
runtime: shiny_prerendered
title: Analyzing RS1 Student Survey Data App
---

```{r setup, include=FALSE}
library(learnr)
load("data/F22_RS1_SurveyData.RData")
knitr::opts_chunk$set(echo = FALSE)
options(scipen=100000)
```

## Selecting Data

**Feel free to change any variables in here inside the code boxes, so you can analyze your data!**

We've gone ahead and loaded the Survey Data for you in R. The data is stored in a variable called `Fall_2022_RS1_SurveyData`.

Below is are the columns for the Survey data.

```{r}
names(Fall_2022_RS1_SurveyData)
```

-   **To select a column to make a graph, use the `$` operator.** So, for example, if you need to select **Hours Slept in the last 24 hours**, you would type `` Fall_2022_RS1_SurveyData$`Hours slept in last 24 hours` ``.

-   Notice that R doesn't like column names with spaces. [To select the column, you need to surround the ENTIRE name with **backtick** marks. On your keyboard, the backtick mark is the key next to **1**. ]{style="background-color: #FFFF00"}

-   [In other words, replace the quotation marks with backtick marks.]{style="background-color: #FFFF00"}

```{r survey_data, exercise=TRUE}
Fall_2022_RS1_SurveyData$`Hours slept in last 24 hours`
```

## Analyzing Categorical Data

### Counting Categorical Data

**Feel free to change any variables in here inside the code boxes, so you can analyze your data!**

Again, below are the columns for the Survey data.

```{r}
names(Fall_2022_RS1_SurveyData)
```

`Teacher` is a categorical variable. This will give you a table with counts of each teacher.

```{r teacher_table, exercise=TRUE}
table(Fall_2022_RS1_SurveyData$`Teacher`)
```

To plot this categorical data, use the `plot` command. (Note that this is only possible because we imported all categorical data here as "factors", but you don't need know what this is, for now)

```{r teacher_bar, exercise=TRUE}
plot(Fall_2022_RS1_SurveyData$`Teacher`, 
     main="Distribution of RS1 Students by Teacher",
     xlab="Teacher", 
     ylab="Number of Students", 
     cex.names=0.9) 
#The cex.names parameter shrinks the text size 
#on the x-axis, which allows all teachers' names to be printed.
#Here, we shrunk the text size to 90% of the original.
```

## Analyzing Quantitative Data

Again, below are the columns for the Survey data.

```{r}
names(Fall_2022_RS1_SurveyData)
```

You can use `mean()`, `median()`, `fivenum()` to find each statistic for the data.

```{r sum, exercise=TRUE}
mean(Fall_2022_RS1_SurveyData$`Miles home is from TJ`)

```

### Making Dotplots

**Feel free to change any variables in here inside the code boxes, so you can analyze your data!**

To make a dotplot out of Quantitative Data, use the following code:

```{r dotplot, exercise=TRUE}
stripchart(Fall_2022_RS1_SurveyData$`Miles home is from TJ`, method = "stack", 
           offset = 1, 
           at = 0, 
           pch = 19,
           col = "steelblue", 
           main = "Average Distance Students are from TJ", 
           xlab = "Distance in Miles")

```

Someone put down 1800 miles. I hope they were talking about from their home country, because that's a lot of miles traveled every day!

### Making Histograms

Here's how to make a plot for the number of shoes each student wears

```{r histogram, exercise=TRUE}
hist(Fall_2022_RS1_SurveyData$`Shoes`, 
     col= "skyblue", 
     main= "Histogram of number of Shoes owned", 
     xlab= "Number of Shoes", 
     ylab="Number of TJ Students")
```

### Making Boxplots

Finally, here's the same data, in a boxplot. Notice all the outliers!

```{r boxplot, exercise=TRUE}
boxplot(Fall_2022_RS1_SurveyData$`Shoes`, 
     col= "skyblue", 
     main= "Number of Shoes owned by TJ Students", 
     xlab= "Number of Shoes", 
     horizontal=T)
```
