---
output: 
  html_document:
    includes:
      in_header: iframe_resizer.html
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
library(readr)
library(gradethis)
gradethis::gradethis_setup()
knitr::opts_chunk$set(echo = FALSE)
```

## Chicken Weights

We will do our first analysis with the `ChickWeight` dataset, already built into R. 

```{r, include=TRUE, echo=TRUE}
data(ChickWeight)
head(ChickWeight)
```

To understand what the data represents, type `?ChickWeight` into the console **in RStudio**. If you are lazy, you can also find the documentation [here.](https://rdocumentation.org/packages/datasets/versions/3.6.2/topics/ChickWeight)  

How many chickens in total were part of this experiment? (Hint: look at the number of rows)



### Summary Exercises
1. Find the average weight of a chicken on any diet on the 18th day of their feeding.

2. Tabulate the total number of chickens that were on each diet.

3. Find the standard deviation of chicken weights on Day 0. Then, do the same for Day 21.

4. Finally, use `dplyr` to find the mean weight and standard deviation of all Chickens on Day 21, grouped by diet. Which diet led to the heaviest chickens? (When you do the summarize function, use `mean_weight` and `std_dev` as your labels).

```{r summ-chicken-setup}
library(datasets)
library(dplyr)
data(ChickWeight)
```

```{r summ-chicken, exercise=TRUE, exercise.cap="Summarizing Chicken Weights Exercise"}
#1

#2

#3

#4

```

```{r summ-chicken-solution}
#1
mean(ChickWeight$weight[ChickWeight$Time %in% 18])

#2
table(ChickWeight$Diet)

#3
sd(ChickWeight$weight[ChickWeight$Time %in% 0])
sd(ChickWeight$weight[ChickWeight$Time %in% 21])

#4
ChickWeight %>%
  dplyr::filter(Time==21) %>%
  dplyr::select(weight, Diet) %>%
  dplyr::group_by(Diet)%>% 
  summarize(mean_weight= mean(weight), std_dev= sd(weight))
```

```{r summ-chicken-hint}
#1
mean(ChickWeight$weight[... %in% ...])

#2
table(...)

#3
sd(...)
sd(...)

#4
ChickWeight %>%
  dplyr::filter(... ) %>%
  dplyr::group_by(...)%>% 
  dplyr::select(...) %>%
  ...(mean_weight= mean(...), std_dev= sd(...))
```

```{r summ-chicken-code-check}
grade_code()
```



### Visualization Exercises
```{r viz-chicken-setup}
library(datasets)
library(dplyr)
data(ChickWeight)
```

Let's move onto practicing making graphs now. 

1. Filter the weight of chicken weights on Day `14` (remember that's the `Time` variable) that were on Diet `3`, and save that as `wt_day14_diet3`. Then graph this variable in a dot plot. Use the following for your parameters:
  + Title: "Weights of Chickens on Diet 3, on Day 14"
  + x-axis: "Weight (grams)"

2. Create a histogram of chicken weights on Day `0` , for any diet. Use the following for your parameters:
  + Title: "Chicken Weights on Day 0"
  + x-axis: "Weight (grams)"
  + y-axis: "Number of Chickens"

3. Create boxplots of chicken weights on Day `21`, grouped by `Diet`. Use the following parameters:
  + Title: "Comparison of Chicken Diets"
  + x-axis: "Diet"
  + y-axis: "Weight (grams)"
  + You should also label each diet as "Diet 1", "Diet 2", and so forth.
  + Colors: From left to right, your boxplots should be "pink", "green", "skyblue", and "purple" respectively.

```{r viz-chicken, exercise=TRUE, exercise.cap="Vizualizing Chicken Weights Exercise"}
#1

#2

#3
```

```{r viz-chicken-hint}
#1
wt_day14_diet3 <- ChickWeight$...[ChickWeight$Time %in% 14 & ...]
stripchart(... , method = "stack", 
           offset = .5, 
           at = 0, 
           pch = 19, 
           main = "...", 
           xlab = "...")

#2
hist(ChickWeight$weight[...],
     main="Chicken Weights on Day 0",
     xlab="Weight (grams)",
     ylab= "Number of Chickens")

#3
boxplot(...~..., data=...,
        main= "Comparison of Chicken Diets",
        xlab= "Diet",
        ylab= "Weight (grams)",
        names= c(...),
        ...= c(...))

```

```{r viz-chicken-solution}
#1
wt_day14_diet3 <- ChickWeight$weight[ChickWeight$Time %in% 14 & ChickWeight$Diet %in% 3]
stripchart(wt_day14_diet3, method = "stack", 
           offset = .5, 
           at = 0, 
           pch = 19, 
           main = "Weights of Chickens on Diet 3, on Day 14", 
           xlab = "Weight (grams)")

#2
hist(ChickWeight$weight[ChickWeight$Time %in% 0],
     main="Chicken Weights on Day 0",
     xlab="Weight (grams)",
     ylab= "Number of Chickens")

#3
boxplot(weight~Diet, data=ChickWeight,
        main= "Comparison of Chicken Diets",
        xlab= "Diet",
        ylab= "Weight (grams)",
        names= c("Diet 1", "Diet 2", "Diet 3", "Diet 4"),
        col= c("pink", "green", "skyblue", "purple"))

```

```{r viz-chicken-code-check}
grade_code()
```